Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-20 paper/ms.tex
submitted version

\bibliographystyle{mn2e}
\bibliography{references}

>>>>

\bibliographystyle{mn2e}
%\bibliography{references} 
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
  et~al.}{2013a}]{Behroozi2013b}
{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013a, \apjl, 762, L31

\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
  et~al.}{2013b}]{Behroozi2013a}
{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013b, \apj, 770, 57

\bibitem[\protect\citeauthoryear{{Colberg}, {White}, {Yoshida}, {MacFarland},
  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
  {Thomas} \& {Virgo Consortium}}{{Colberg} et~al.}{2000}]{Colberg00}
{Colberg} J.~M.,  {White} S.~D.~M.,  {Yoshida} N.,  {MacFarland} T.~J.,
  {Jenkins} A.,  {Frenk} C.~S.,  {Pearce} F.~R.,  {Evrard} A.~E.,  {Couchman}
  H.~M.~P.,  {Efstathiou} G.,  {Peacock} J.~A.,  {Thomas} P.~A.,    {Virgo
  Consortium} 2000, \mnras, 319, 209

\bibitem[\protect\citeauthoryear{{Dayal}, {Ferrara}, {Saro}, {Salvaterra},
  {Borgani} \& {Tornatore}}{{Dayal} et~al.}{2009}]{Dayal2009}
{Dayal} P.,  {Ferrara} A.,  {Saro} A.,  {Salvaterra} R.,  {Borgani} S.,
  {Tornatore} L.,  2009, \mnras, 400, 2000

\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
  {Kramer}}{2012}]{Dijkstra2012}
{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672

\bibitem[\protect\citeauthoryear{{Dijkstra}, {Mesinger} \& {Wyithe}}{{Dijkstra}
  et~al.}{2011}]{Dijkstra11}
{Dijkstra} M.,  {Mesinger} A.,    {Wyithe} J.~S.~B.,  2011, \mnras, 414, 2139

\bibitem[\protect\citeauthoryear{{Forero-Romero} \& {Dijkstra}}{{Forero-Romero}
  \& {Dijkstra}}{2013}]{ForeroRomero2013}
{Forero-Romero} J.~E.,  {Dijkstra} M.,  2013, \mnras, 428, 2163

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero}
  et~al.}{2011}]{ForeroRomero2011}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber} \&
  {Prada}}{{Forero-Romero} et~al.}{2012}]{ForeroRomero2012}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,    {Prada} F.,  2012,
  \mnras, 419, 952

\bibitem[\protect\citeauthoryear{{Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
  {Verhamme} \& {Hayes}}{{Garel} et~al.}{2012}]{Garel2012}
{Garel} T.,  {Blaizot} J.,  {Guiderdoni} B.,  {Schaerer} D.,  {Verhamme} A.,
  {Hayes} M.,  2012, \mnras, 422, 310

\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio} \&
  {Feldmeier}}{{Gawiser} et~al.}{2007}]{Gawiser2007}
{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
  G.~A.,  {Fazio} G.,    {Feldmeier} J.~J.,  2007, \apj, 671, 278

\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio},
  {Feldmeier}, {Huang}, {Infante}, {Lira} \& {Padilla}}{{Gawiser}
  et~al.}{2007}]{Gawiser07}
{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
  G.~A.,  {Fazio} G.,  {Feldmeier} J.~J.,  {Huang} J.-s.,  {Infante} L.,
  {Lira} P.,    {Padilla} N.,  2007, \apj, 671, 278

\bibitem[\protect\citeauthoryear{{Gronwall}, {Ciardullo}, {Hickey}, {Gawiser},
  {Feldmeier}, {van Dokkum}, {Urry}, {Herrera}, {Lehmer}, {Infante}, {Orsi},
  {Marchesini}, {Blanc}, {Francke}, {Lira} \& {Treister}}{{Gronwall}
  et~al.}{2007}]{Gronwall07}
{Gronwall} C.,  {Ciardullo} R.,  {Hickey} T.,  {Gawiser} E.,  {Feldmeier}
  J.~J.,  {van Dokkum} P.~G.,  {Urry} C.~M.,  {Herrera} D.,  {Lehmer} B.~D.,
  {Infante} L.,  {Orsi} A.,  {Marchesini} D.,  {Blanc} G.~A.,  {Francke} H.,
  {Lira} P.,    {Treister} E.,  2007, \apj, 667, 79

\bibitem[\protect\citeauthoryear{{Guaita}, {Francke}, {Gawiser}, {Bauer},
  {Hayes}, {{\"O}stlin} \& {Padilla}}{{Guaita} et~al.}{2013}]{Guaita2013}
{Guaita} L.,  {Francke} H.,  {Gawiser} E.,  {Bauer} F.~E.,  {Hayes} M.,
  {{\"O}stlin} G.,    {Padilla} N.,  2013, \aap, 551, A93

\bibitem[\protect\citeauthoryear{{Hayashino}, {Matsuda}, {Tamura}, {Yamauchi},
  {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi},
  {Shimasaku}, {Shioya} \& {Taniguchi}}{{Hayashino}
  et~al.}{2004}]{Hayashino2004}
{Hayashino} T.,  {Matsuda} Y.,  {Tamura} H.,  {Yamauchi} R.,  {Yamada} T.,
  {Ajiki} M.,  {Fujita} S.~S.,  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,
  {Okamura} S.,  {Ouchi} M.,  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,
  2004, \aj, 128, 2073

\bibitem[\protect\citeauthoryear{{Jarosik}, {Bennett}, {Dunkley}, {Gold},
  {Greason}, {Halpern}, {Hill}, {Hinshaw}, {Kogut}, {Komatsu}, {Larson} \&
  {Limon}}{{Jarosik} et~al.}{2011}]{Jarosik2011}
{Jarosik} N.,  {Bennett} C.~L.,  {Dunkley} J.,  {Gold} B.,  {Greason} M.~R.,
  {Halpern} M.,  {Hill} R.~S.,  {Hinshaw} G.,  {Kogut} A.,  {Komatsu} E.,
  {Larson} D.,    {Limon} M.,  2011, \apjs, 192, 14

\bibitem[\protect\citeauthoryear{{Jose}, {Srianand} \& {Subramanian}}{{Jose}
  et~al.}{2013}]{Jose2013b}
{Jose} C.,  {Srianand} R.,    {Subramanian} K.,  2013, ArXiv e-prints

\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
  {Primack}}{{Klypin} et~al.}{2011}]{Bolshoi}
{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102

\bibitem[\protect\citeauthoryear{{Koehler}, {Schuecker} \&
  {Gebhardt}}{{Koehler} et~al.}{2007}]{Koehler2007}
{Koehler} R.~S.,  {Schuecker} P.,    {Gebhardt} K.,  2007, \aap, 462, 7

\bibitem[\protect\citeauthoryear{{Komatsu}, {Dunkley}, {Nolta}, {Bennett},
  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Limon}, {Page}, {Spergel} \&
  {Halpern}}{{Komatsu} et~al.}{2009}]{Komatsu2009}
{Komatsu} E.,  {Dunkley} J.,  {Nolta} M.~R.,  {Bennett} C.~L.,  {Gold} B.,
  {Hinshaw} G.,  {Jarosik} N.,  {Larson} D.,  {Limon} M.,  {Page} L.,
  {Spergel} D.~N.,    {Halpern} M.,  2009, \apjs, 180, 330

\bibitem[\protect\citeauthoryear{{Kudritzki}, {M{\'e}ndez}, {Feldmeier},
  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard} \&
  {Ford}}{{Kudritzki} et~al.}{2000}]{Kudritzki2000}
{Kudritzki} R.-P.,  {M{\'e}ndez} R.~H.,  {Feldmeier} J.~J.,  {Ciardullo} R.,
  {Jacoby} G.~H.,  {Freeman} K.~C.,  {Arnaboldi} M.,  {Capaccioli} M.,
  {Gerhard} O.,    {Ford} H.~C.,  2000, \apj, 536, 19

\bibitem[\protect\citeauthoryear{{Landy} \& {Szalay}}{{Landy} \&
  {Szalay}}{1993}]{Landy1993}
{Landy} S.~D.,  {Szalay} A.~S.,  1993, \apj, 412, 64

\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
  et~al.}{2013}]{Laursen2013}
{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124

\bibitem[\protect\citeauthoryear{{Laursen}, {Razoumov} \&
  {Sommer-Larsen}}{{Laursen} et~al.}{2009}]{Laursen2009}
{Laursen} P.,  {Razoumov} A.~O.,    {Sommer-Larsen} J.,  2009, \apj, 696, 853

\bibitem[\protect\citeauthoryear{{Laursen} \& {Sommer-Larsen}}{{Laursen} \&
  {Sommer-Larsen}}{2007}]{Laursen2007}
{Laursen} P.,  {Sommer-Larsen} J.,  2007, \apjl, 657, L69

\bibitem[\protect\citeauthoryear{{Matsuda}, {Yamada}, {Hayashino}, {Tamura},
  {Yamauchi}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi}, {Shimasaku},
  {Shioya} \& {Taniguchi}}{{Matsuda} et~al.}{2005}]{Matsuda2005}
{Matsuda} Y.,  {Yamada} T.,  {Hayashino} T.,  {Tamura} H.,  {Yamauchi} R.,
  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,  {Okamura} S.,  {Ouchi} M.,
  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,  2005, \apjl, 634, L125

\bibitem[\protect\citeauthoryear{{More}, {Kravtsov}, {Dalal} \&
  {Gottl{\"o}ber}}{{More} et~al.}{2011}]{More2011}
{More} S.,  {Kravtsov} A.~V.,  {Dalal} N.,    {Gottl{\"o}ber} S.,  2011, \apjs,
  195, 4

\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{Neufeld1991}
{Neufeld} D.~A.,  1991, \apjl, 370, L85

\bibitem[\protect\citeauthoryear{{Nilsson}, {M{\o}ller}, {M{\"o}ller}, {Fynbo},
  {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen} \&
  {Grove}}{{Nilsson} et~al.}{2007}]{Nilsson2007}
{Nilsson} K.~K.,  {M{\o}ller} P.,  {M{\"o}ller} O.,  {Fynbo} J.~P.~U.,
  {Micha{\l}owski} M.~J.,  {Watson} D.,  {Ledoux} C.,  {Rosati} P.,  {Pedersen}
  K.,    {Grove} L.~F.,  2007, \aap, 471, 71

\bibitem[\protect\citeauthoryear{{Nilsson}, {Tapken}, {M{\o}ller}, {Freudling},
  {Fynbo}, {Meisenheimer}, {Laursen} \& {{\"O}stlin}}{{Nilsson}
  et~al.}{2009}]{Nilsson2009}
{Nilsson} K.~K.,  {Tapken} C.,  {M{\o}ller} P.,  {Freudling} W.,  {Fynbo}
  J.~P.~U.,  {Meisenheimer} K.,  {Laursen} P.,    {{\"O}stlin} G.,  2009, \aap,
  498, 13

\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
  et~al.}{2012}]{Orsi2012}
{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87

\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
  {Okamura}, {Iye}, {Takata}, {Yoshida} \& {Yoshida}}{{Ouchi}
  et~al.}{2008}]{Ouchi2008}
{Ouchi} M.,  {Shimasaku} K.,  {Akiyama} M.,  {Simpson} C.,  {Saito} T.,  {Ueda}
  Y.,  {Furusawa} H.,  {Sekiguchi} K.,  {Yamada} T.,  {Kodama} T.,  {Kashikawa}
  N.,  {Okamura} S.,  {Iye} M.,  {Takata} T.,  {Yoshida} M.,    {Yoshida} M.,
  2008, \apjs, 176, 301

\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
  {Okamura}, {Simpson} \& {Yoshida}}{{Ouchi} et~al.}{2010}]{Ouchi2010}
{Ouchi} M.,  {Shimasaku} K.,  {Furusawa} H.,  {Saito} T.,  {Yoshida} M.,
  {Akiyama} M.,  {Ono} Y.,  {Yamada} T.,  {Ota} K.,  {Kashikawa} N.,  {Iye} M.,
   {Kodama} T.,  {Okamura} S.,  {Simpson} C.,    {Yoshida} M.,  2010, \apj,
  723, 869

\bibitem[\protect\citeauthoryear{{Peebles}}{{Peebles}}{1980}]{Peebles1980}
{Peebles} P.~J.~E.,  1980, {The large-scale structure of the universe}

\bibitem[\protect\citeauthoryear{{Pentericci}, {Grazian}, {Fontana},
  {Castellano}, {Giallongo}, {Salimbeni} \& {Santini}}{{Pentericci}
  et~al.}{2009}]{Pentericci2009}
{Pentericci} L.,  {Grazian} A.,  {Fontana} A.,  {Castellano} M.,  {Giallongo}
  E.,  {Salimbeni} S.,    {Santini} P.,  2009, \aap, 494, 553

\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
  Granger}{2007}]{IPython}
P\'erez F.,  Granger B.~E.,  2007, {C}omput. {S}ci. {E}ng., 9, 21

\bibitem[\protect\citeauthoryear{Riebe, Partl, Enke, Forero-Romero, Gottlöber,
  Klypin, Lemson, Prada, Primack, Steinmetz \& Turchaninov}{Riebe
  et~al.}{2013}]{MultiDark}
Riebe K.,  Partl A.~M.,  Enke H.,  Forero-Romero J.,  Gottlöber S.,  Klypin
  A.,  Lemson G.,  Prada F.,  Primack J.~R.,  Steinmetz M.,    Turchaninov V.,
  2013, Astronomische Nachrichten, 334, 691

\bibitem[\protect\citeauthoryear{{Springel}, {White}, {Jenkins}, {Frenk},
  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
  {Thomas}, {Couchman}, {Evrard}, {Colberg} \& {Pearce}}{{Springel}
  et~al.}{2005}]{SpringelNature05}
{Springel} V.,  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,  {Yoshida} N.,
   {Gao} L.,  {Navarro} J.,  {Thacker} R.,  {Croton} D.,  {Helly} J.,
  {Peacock} J.~A.,  {Cole} S.,  {Thomas} P.,  {Couchman} H.,  {Evrard} A.,
  {Colberg} J.,    {Pearce} F.,  2005, \nat, 435, 629

\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
  {Maselli}}{{Verhamme} et~al.}{2006}]{Verhamme2006}
{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397

\bibitem[\protect\citeauthoryear{{Walker-Soler}, {Gawiser}, {Bond}, {Padilla}
  \& {Francke}}{{Walker-Soler} et~al.}{2012}]{Soler2012}
{Walker-Soler} J.~P.,  {Gawiser} E.,  {Bond} N.~A.,  {Padilla} N.,    {Francke}
  H.,  2012, \apj, 752, 160

\bibitem[\protect\citeauthoryear{{Yajima}, {Choi} \& {Nagamine}}{{Yajima}
  et~al.}{2012}]{Yajima2012}
{Yajima} H.,  {Choi} J.-H.,    {Nagamine} K.,  2012, \mnras, 427, 2889

\bibitem[\protect\citeauthoryear{{Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
  {Yamauchi}, {Morimoto}, {Kousai} \& {Umemura}}{{Yamada}
  et~al.}{2012}]{Yamada2012}
{Yamada} T.,  {Nakamura} Y.,  {Matsuda} Y.,  {Hayashino} T.,  {Yamauchi} R.,
  {Morimoto} N.,  {Kousai} K.,    {Umemura} M.,  2012, \aj, 143, 79

\bibitem[\protect\citeauthoryear{{Zheng}, {Cen}, {Trac} \&
  {Miralda-Escud{\'e}}}{{Zheng} et~al.}{2010}]{Zheng2010}
{Zheng} Z.,  {Cen} R.,  {Trac} H.,    {Miralda-Escud{\'e}} J.,  2010, \apj,
  716, 574

\end{thebibliography}
